### 2017-12-26 icde/revision/sec-model.tex

%However, the resulting author citation graph to compute the prestige is typically too large to handle.
\markedb{To evaluate the importance of each author, an author citation graph needs firstly to be constructed such that (a) a node represents an author, and (b) a direct edge $(s,t)$ denotes that there exist articles published by author $s$ citing articles published by author $t$. It is not hard to image that the number of edges in the author citation graph is much larger than the number in the citation graph, which reaches xxx on \magdata. Handing such a graph is computationally expensive. }
Hence, we evaluate the prestige of an author, by using the average prestige of all articles published by the author. Similar to the venue component, the popularity of an author is also defined as the average popularity of her/his published articles. Finally, the prestige and popularity are combined to derive the importance in the same way as the citation component.

>>>>

%However, the resulting author citation graph to compute the prestige is typically too large to handle.
\markedb{To evaluate the importance of each author, an author citation graph needs firstly to be constructed such that (a) a node represents an author, and (b) a direct edge $(s,t)$ denotes that there exist articles published by author $s$ citing articles published by author $t$. It is not hard to image that the number of edges in the author citation graph is much larger than the number in the citation graph, which reaches to 4.5 billion on \magdata. Handing such a graph is computationally expensive. }
Hence, we evaluate the prestige of an author, by using the average prestige of all articles published by the author. Similar to the venue component, the popularity of an author is also defined as the average popularity of her/his published articles. Finally, the prestige and popularity are combined to derive the importance in the same way as the citation component.
